\documentclass[11pt, letterpaper]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{inputenc}
\usepackage{titlesec}
\usepackage{parskip}

\hypersetup{
    colorlinks=true,
    urlcolor=black,
}

% Section formatting
\titleformat{\section}
  {\bfseries\normalsize}
  {}
  {0em}
  {}
  [\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

\setlength{\parindent}{0pt}
\pagestyle{empty}

% Custom commands
\newcommand{\employer}[4]{%
  \textbf{#1} $|$ #2 \hfill \textbf{#3} \\
  \textit{#4}
}

\newcommand{\school}[4]{%
  \textbf{#1} $|$ #2 \hfill \textbf{#3} \\
  #4
}

\newcommand{\project}[3]{%
  \textbf{#1} \hfill \textit{#2} \\
  #3
}

\begin{document}

% ── Header ──────────────────────────────────────────────────────────────────
\begin{center}
  {\Large\bfseries PRANSHU NITIN BHEDA} \\[4pt]
  pb2053@rit.edu \; $|$ \; +1 (917) 794-8716 \; $|$ \;
  \href{https://pranshubheda.github.io/}{https://pranshubheda.github.io/}
\end{center}

% ── Education ───────────────────────────────────────────────────────────────
\section{EDUCATION}

\school{Rochester Institute of Technology}{Rochester, NY}{May 2020}{Master of Science, Computer Science \quad GPA: 3.67/4}

\medskip

\school{Thakur College of Engineering \& Technology}{Mumbai, India}{May 2017}{Bachelor of Engineering, Information Technology \quad GPA: 7.44/10}

% ── Work Experience ─────────────────────────────────────────────────────────
\section{WORK EXPERIENCE}

\employer{SoFi}{Seattle, USA}{Aug 2024 -- Present}{Senior Software Engineer, Machine Learning Platform}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=4pt]
  \item Architect and implement internal frameworks that streamlined the end-to-end ML lifecycle at SoFi.
  \item Developed internal frameworks for feature engineering, model building, training, and deployment that support both real-time (online) and batch (offline) inference use cases.
\end{itemize}

\medskip

\employer{SoFi}{Seattle, USA}{Aug 2022 -- Aug 2024}{Senior Software Engineer, Identity}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=4pt]
  \item Improve availability and resiliency of service by implementing automated failover mechanism for critical tier-1 services that handle login and registration.
\end{itemize}

\medskip

\employer{SoFi}{Seattle, USA}{May 2022 -- Aug 2023}{Software Engineer, Identity}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=4pt]
  \item Full-stack development using Java and JavaScript on tier-1 services that handle login, registration, two-factor authentication and authorization for millions of users at a top financial institution.
  \item Contributed to building an authorization server to power SoFi travel experience.
  \item Contributed to building a framework to gather device intelligence for a user session to enable data driven risk profiling.
\end{itemize}

\medskip

\employer{MathWorks}{Natick, USA}{May 2020 -- May 2022}{Software Engineer, Install \& Licensing}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=4pt]
  \item Full-stack development on MathWorks Product Installer using JavaScript on the frontend and C++ on the backend.
  \item Contributed to the design of an event driven architecture to make the installer data driven while migrating legacy code.
  \item Developed the progress panel widget and the logic to handle back and forth navigation in the installer.
\end{itemize}

% ── Technical Skills ─────────────────────────────────────────────────────────
\section{TECHNICAL SKILLS}

\textbf{Programming Languages:} C, C++, Java, Python, JavaScript, MATLAB, Kotlin \\
\textbf{Devops:} Kubernetes, Docker, Datadog, Cloudflare, AWS \\
\textbf{UI Development:} AngularJS, React, DOJO, Lit, Web Components, HTML, CSS \\
\textbf{Data Engineering:} Pentaho Data Integration \\
\textbf{Database:} MySQL, Neo4j, Apache Jena, Oracle, PostgreSQL, MongoDB, SPARQL, Cypher, GraphQL

% ── Projects ────────────────────────────────────────────────────────────────
\section{PROJECTS}

\project{MATLAB Blockly}{3\textsuperscript{rd} Place Hackathon}{}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=4pt]
  \item Developed a block based visual programming editor enabling users to generate MATLAB code by connecting blocks of code together like a puzzle to build programs. Helps overcome the initial syntax barrier in introductory programming assignments. \\
        \textit{Stack: MATLAB, JavaScript}
\end{itemize}

\medskip

\project{GPS Data Analysis}{Academic}{}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=4pt]
  \item Analysis of GPS data collected from an Arduino connected to a car to identify the best route from given source to destination.
  \item Involved data cleaning, data clustering and objective function minimization to identify the best route. \\
        \textit{Stack: Python, Pandas, SK Learn}
\end{itemize}

\medskip

\project{Social Network Analysis -- DBLP Dataset}{Academic}{}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=4pt]
  \item Creating a co-author network from an XML dump and loading the derived network in a Neo4j database for effective querying. Analyzing the derived network using graph theory to identify collaboration patterns amongst research communities. \\
        \textit{Stack: Java, MySQL, MongoDB, Neo4j}
\end{itemize}

\medskip

\project{Machine Learning on Graphs}{Academic}{}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=4pt]
  \item Graph representation learning using the TransE algorithm followed by link prediction using the IMDB knowledge graph. \\
        \textit{Stack: Java, Apache Jena}
\end{itemize}

\medskip

\project{Mobile Robot Programming -- Pioneer P3-DX}{Academic}{}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=4pt]
  \item Implemented occupancy grid mapping, particle filter localization and theta star path planning algorithm using laser scan and sonar sensors. \\
        \textit{Stack: ROS, Python}
\end{itemize}

\medskip

\project{Quantum Algorithms}{Academic}{}
\begin{itemize}[leftmargin=1.5em, itemsep=0pt, topsep=4pt]
  \item Developed and presented a seminar in quantum algorithms, Fall 2019 -- Deutsch-Jozsa Algorithm.
\end{itemize}

\end{document}
